%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sai Srujan Punati} \\ \vspace{1pt}
    \small Hyderabad, India $|$
    \href{tel:+917569799199}{\underline{+91 75697 99199}} $|$
    \href{mailto:saisrujanpunati@gmail.com}{\underline{Email}} $|$
    \href{https://linkedin.com/in/saisrujanpunati}{\underline{LinkedIn}} $|$
    \href{https://github.com/saiusesgithub}{\underline{GitHub}} $|$
    \href{https://saisrujan.is-a.dev}{\underline{Portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Vidya Jyothi Institute of Technology}{Hyderabad, India}
      {Bachelor of Technology in Information Technology; CGPA: 9.38/10}{Aug. 2024 -- May 2028}

    \resumeSubheading
      {NSR Impulse Junior College}{Hyderabad, India}
      {Intermediate, MPC; Percentage: 94.7\%}{2022 -- 2024}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
    {\href{https://startupsindia.in}{\underline{Startups India}}}{Hyderabad}
    {App Development Lead Intern \textnormal{\textbar{} On-site}}{Jul. 2026 -- Present}


\resumeSubSubheading
  {Freelance App Developer \textnormal{\textbar{} Remote}}{Apr. 2026 -- Jul. 2026}

\resumeItemListStart

  \resumeItem{Solely designed, architected, and developed a production-ready cross-platform Flutter application for India's startup ecosystem, owning the complete product lifecycle from requirements gathering and system design through development, testing, CI/CD, and Play Store preparation.}


\resumeItem{Architected a modular, production-grade Flutter application using Riverpod, the Repository Pattern, Firebase Authentication, Cloud Firestore, and Cloudinary, while implementing backend integrations and GitHub Actions CI/CD pipelines for automated testing, build generation, and release delivery.}


  \resumeItem{Collaborated directly with stakeholders to gather requirements, iterate on product feedback and improve platform scalability}

\resumeItemListEnd



\resumeSubheading
  {\textbf{Elite Coders Summer of Code 2026} $|$
  \href{https://prism-bits.vercel.app/}{\underline{Website}} $|$
  \href{https://github.com/saiusesgithub/Prism-Bits}{\underline{GitHub}}}
  {Remote}
  {Project Admin \& Maintainer — Prism Bits}
  {Jul. 2026 -- Present}

\resumeItemListStart

  \resumeItem{Founded and maintain Prism Bits, an extensible open-source, multi-framework UI component library built around reusable, source-first components that developers can preview, copy, customize, and integrate into production interfaces.}

  \resumeItem{Manage the complete open-source contribution lifecycle by defining issues, assigning contributors, reviewing pull requests, providing technical feedback, enforcing code-quality and registry-validation standards, merging contributions, mentoring first-time contributors, and continuously improving the Next.js and TypeScript codebase.}

\resumeItemListEnd

\resumeSubheading
  {\textbf{E-Cell VJIT} $|$
  \href{https://ecell-pre-production.vercel.app/}{\underline{Live}} $|$
  \href{https://github.com/ECell-VJIT/ECell-Website}{\underline{GitHub}}}
  {Hyderabad}
  {Technical Lead}
  {Feb. 2026 -- Present}

\resumeItemListStart

  \resumeItem{Lead the architecture and development of E-Cell VJIT's full-stack platform using Astro, TypeScript, Node.js serverless functions, Supabase PostgreSQL, Cloudflare R2, Cloudinary, and Vercel, overseeing feature delivery, deployment, and technical coordination.}

  \resumeItem{Engineered an end-to-end event automation system covering registrations, payments, confirmation emails, QR-based PDF ticket generation, browser-based attendance scanning, admin workflows, and automated certificate generation using Maileroo, qrcode, pdf-lib, Puppeteer, and html5-qrcode.}

\resumeItemListEnd

\resumeSubheading
  {\textbf{DevUp Society, VJIT} $|$
  \href{https://devupvjit.in}{\underline{Live}} $|$
  \href{https://github.com/DevUp-Society/DevUp-Society-Website}{\underline{GitHub}}}
  {Hyderabad}
  {Technical Lead}
  {Sep. 2025 -- Present}

\resumeItemListStart

  \resumeItem{Solely designed and developed DevUp Society's production website and event platform, owning UI/UX, frontend architecture, backend workflows, deployment, domain configuration, and ongoing maintenance.}

  \resumeItem{Built event registration, payment-verification, admin approval, automated email, and ticket-generation workflows supporting technical events attended by 200+ participants.}

\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Startups India Media Platform} $|$
      \href{https://github.com/saiusesgithub/StartupsIndia-MediaPlatform}{\underline{GitHub}}}
      {}

      \resumeItemListStart
        \resumeItem{\textit{Flutter, Firebase, Firestore, Riverpod, Cloudinary, GitHub Actions} — Designed and developed a production-ready cross-platform application as the sole app developer, owning architecture, backend integration, testing, release workflows, and Play Store preparation.}

        \resumeItem{Built a modular codebase using Riverpod and the Repository Pattern, with Firebase Authentication, Cloud Firestore, Cloudinary media delivery, and automated CI/CD release builds.}
      \resumeItemListEnd


    \resumeProjectHeading
      {\textbf{Student Platforms \& Event Automation} $|$
      \href{https://devupvjit.in}{\underline{DevUp}} $|$
      \href{https://ecell-pre-production.vercel.app/}{\underline{E-Cell}}}
      {}

      \resumeItemListStart
        \resumeItem{\textit{Astro, TypeScript, Node.js, Supabase, Cloudflare R2, Vercel} — Solely designed and developed both platforms, owning UI/UX, frontend architecture, serverless workflows, database integration, deployment, and maintenance.}

        \resumeItem{Built registration, admin approval, payment verification, automated email, QR ticketing, attendance scanning, and certificate-generation workflows; supported DevUp events with 200+ participants.}
      \resumeItemListEnd


    \resumeProjectHeading
      {\textbf{Cloud Infrastructure \& Observability Pipeline} $|$
      \href{https://github.com/saiusesgithub/Portfolio}{\underline{GitHub}}}
      {}

      \resumeItemListStart
        \resumeItem{\textit{AWS, Docker, Terraform, Ansible, GitHub Actions, Prometheus, Grafana} — Built an Infrastructure-as-Code and CI/CD pipeline for deploying a containerized portfolio application on AWS.}

        \resumeItem{Automated EC2 provisioning, configuration management, Docker deployment, Prometheus and Node Exporter monitoring, Grafana dashboards, and Discord alerts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------

 \section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, Dart, JavaScript, TypeScript, SQL, HTML, CSS} \\
     \textbf{Frameworks \& Libraries}{: Flutter, React, Next.js, Astro, Node.js, FastAPI, Flask, Riverpod, Tailwind CSS} \\
     \textbf{Backend \& Databases}{: REST APIs, Firebase, Supabase, PostgreSQL, MySQL, SQLite, Vercel Serverless Functions} \\
     \textbf{Cloud \& DevOps}{: AWS, Google Cloud, Oracle Cloud Infrastructure, Docker, Terraform, Ansible, GitHub Actions, GitLab CI/CD, Prometheus, Grafana} \\
     \textbf{Tools \& Platforms}{: Git, GitHub, GitLab, Linux, Vercel, Cloudflare, Cloudinary, Postman}
    }}
 \end{itemize}

%-------------------------------------------

\section{Achievements}
  \resumeItemListStart

    \resumeItem{\textbf{Ranked 6th among 5,000+ developers} in Elite Coders Winter of Code 2026, earning a position among the program's Top 10 open-source contributors.}

    \resumeItem{\textbf{1st Prize — Git Arcana, CBIT}: Won a competitive Git and GitHub problem-solving event focused on version-control workflows and repository operations.}

    \resumeItem{\textbf{2nd Prize — Cyberonix Cybersecurity Hackathon}: Placed second among 200+ participants in a time-bound CTF covering network analysis, cryptography, and steganography.}

    \resumeItem{\textbf{2× 2nd Prize — PitchQuest}: Secured second place in consecutive editions in 2024 and 2025 for the projects MyCloset and ShadowMesh.}

  \resumeItemListEnd

%-------------------------------------------

\section{Certifications \& Credentials}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Harvard CS50x, CS50P \& CS50 SQL} $|$ 
    \textbf{OCI 2025 Certified Foundations Associate} \\
    \textbf{AWS Cloud Quest: Cloud Practitioner} $|$
    \textbf{Build Infrastructure with Terraform on Google Cloud} $|$
    \textbf{Intel Partner Technical Pro – Cloud DevOps}
  }}
\end{itemize}


%-------------------------------------------
\end{document}
